Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-24 outputs/paper/paper.Rmd
update

### perceived ES security features [reference!!!]

The perceived ES security is this paper's dependent variable. According to Levent et al. (2005), enterprise security plan serves as an essential role to coordinate information security policies and applicable security technologies, making them align with the business rules and the developing information models and technical architectures. Consoli (2012) combined acknowledged definitions of context and security, and concluded the security context should point to five goals:Integrity to ensure that data is in the original format and not modified; Confidentiality to ensure that only authorized people have access to resources; Authentication for allowing the access to the resources; Availability to maintain the proper functioning of the information system; Non-repudiation to ensure that a transaction cannot be denied.

@@

### Molibe device security issue features [references!!!]

A mobile device refers to any portable device which has computing and storage capabilities(Singh & Ranjan, 2016). The range of devices from smartphones, iPads, and tablets is quite popular among clients and IT professionals. Mobile users can work everywhere without being constrained by any networking system. These mobility and roaming features extend the network boundary beyond a single fixed point but make security management a much harder issue, because users cannot be tracked down into a fixed location anymore (Al Ladan, 2016). Moreover, mobile devices’ operational systems are highly vulnerable, which results in threats having a variety of ways to spread. There is no device whose platform is completely closed, which has weakened the security performance of the original application and creates more risks for information sharing (Hermann & Fabian, 2014).  There are six independent variables which might affect the perceived ES security:

@@

### Wireless network security issue features [reference!!!]

Mobile communication is generated mainly through radio signals rather than wires, so mobile ES has particular challenges compared with traditional computer-based ES. First of all, reliable Internet availability is a pre-requirement for the secure wireless network. According to Hermann and Fabian (2014), “the wireless network is more accessible to intercept and attack, so traditional security technologies such as firewalls, authentication servers, biometrics, cryptography, intrusion detection, and VPNs are not enough to address security issues in the wireless network”(Hermann & Fabian, 2014). There are six independent variables related to the wireless network which might affect the perceived ES security:

@@

The appearance of cloud computing is narrowing down the gap between mobile ES and small to medium companies. Although it does cut down the set-up process time and cost and reduces the required skills in the company, some challenges and problems should still be kept in mind. Certain loopholes in its architecture have made cloud computing vulnerable to various security and privacy threats (Picek, Mijac, & Androcec, 2017).There are six independent variables related to the cloud computing which might affect the perceived ES security:

@@

### Application level security issue features
The application-level mobile solution mainly consists of mobile operation systems and mobile applications. The application layer provides users with an interface to operate their mobile devices. The operation system act as a platform to run mobile applications. Application-level issues usually take place in a multi-tenant environment or in a virtualized world. There are six independent variables related to the application which might affect the perceived ES security:

@@

### Data Level Security Issue features
Since there is currently no appropriate regulation around data protection, data-level security is relying heavily on trust between the business and the provider. Data location and replication is one of the biggest concerns in the data level. A replica might be located in different countries where there is no clear legislation about data security and privacy, increasing the difficulty of managing the data (Kouatli, 2014). There are six independent variables related to the data access which might affect the perceived ES security:

@@

@@

In this model result, the intercept (-0.086) represents the average effect for the reference group. There is only one reference group : **Treat: treat 0 (using Android devices)**

The coefficient for **treatment effect** is 0.056, suggesting that the average perceived security from people who use iPhone is on average 0.056 unit higher than those who use Android, holding other variables constant. However the p value is 0.622991, which indicates this is not a significant result.

@@

The coefficient for **weak_authentication** is -0.155, suggesting that one unit increase in weak_authentication score is associated with 0.155 unit decrease in the perceived ES security, holding other variables constant.The p value is 0.021122, which indicates this is a significant result. 
```{r model,fig.cap = "regression model result",echo=FALSE, warning=FALSE,fig.width=5, fig.height=8}
## regression

propensity_score_regression <- lm(PSave~ Install_firewall+BYOD+ Ignore_warnning+Strong_pin+
                                    Store_passwords+update_OS+public_WiFi+unsecured_network+
                                    network_control+network_attack+encrypted_transimittion+unreliable_int+
                                    cloud_resource +cloud_compute+remote_datastore+Data_regulation+multiple_login+
                                    weak_authentication+unknown_app+  update_ES+ Auto_update+
                                    VPN + third_party_app+update+single_authenticate+audit_log+access_right+ change_data+ malicious_attack +Data_threats+treat,
                                  data = dta_m)

library(modelsummary)
ms<-
modelsummary(
propensity_score_regression,
output = "default",
fmt = 3,
estimate = "estimate",
statistic = "std.error",
vcov = NULL,
conf_level = 0.95, #confidence level to use for confidence intervals
stars = TRUE,
align = NULL,
notes = NULL,
title = "Regression results")
ms%>%
  kableExtra::kable_styling(bootstrap_options = "basic",
                            latex_options = "HOLD_position",
                            table.envir = "table",
                            font_size =5
                       )

@@

@@

@@

* Do not use public Wi-Fi to operate any mobile ERP system (such as Wi-Fi in coffee shops, airport kiosks or other hotspots).
* Pay attention to wireless network security warnings that pop up on mobile devices
* Keep your web browser, wireless firewall, and anti-virus software up to date.

@@

## Android user's average perceived ES security is higher!

@@

# Appendix {-}

# Additional details

>>>>

### perceived ES security features

The perceived ES security is this paper's dependent variable. According to [@ertaul2005enterprise], enterprise security plan serves as an essential role to coordinate information security policies and applicable security technologies, making them align with the business rules and the developing information models and technical architectures. [@consoli2012corporate] combined acknowledged definitions of context and security, and concluded the security context should point to five goals:Integrity to ensure that data is in the original format and not modified; Confidentiality to ensure that only authorized people have access to resources; Authentication for allowing the access to the resources; Availability to maintain the proper functioning of the information system; Non-repudiation to ensure that a transaction cannot be denied.

@@

### Molibe device security issue features

A mobile device refers to any portable device which has computing and storage capabilities [@singh2016framework]. The range of devices from smartphones, iPads, and tablets is quite popular among clients and IT professionals. Mobile users can work everywhere without being constrained by any networking system. These mobility and roaming features extend the network boundary beyond a single fixed point but make security management a much harder issue, because users cannot be tracked down into a fixed location anymore [@singh2016framework]. Moreover, mobile devices’ operational systems are highly vulnerable, which results in threats having a variety of ways to spread. There is no device whose platform is completely closed, which has weakened the security performance of the original application and creates more risks for information sharing[@hermann2014comparison].  There are six independent variables which might affect the perceived ES security:

@@

### Wireless network security issue features

Mobile communication is generated mainly through radio signals rather than wires, so mobile ES has particular challenges compared with traditional computer-based ES. First of all, reliable Internet availability is a pre-requirement for the secure wireless network. According to [@hermann2014comparison], “the wireless network is more accessible to intercept and attack, so traditional security technologies such as firewalls, authentication servers, biometrics, cryptography, intrusion detection, and VPNs are not enough to address security issues in the wireless network”[@hermann2014comparison]. There are six independent variables related to the wireless network which might affect the perceived ES security:

@@

The appearance of cloud computing is narrowing down the gap between mobile ES and small to medium companies. Although it does cut down the set-up process time and cost and reduces the required skills in the company, some challenges and problems should still be kept in mind. Certain loopholes in its architecture have made cloud computing vulnerable to various security and privacy threats [@picek2017acceptance].There are six independent variables related to the cloud computing which might affect the perceived ES security:

@@

### Application level security issue features
The application-level mobile solution mainly consists of mobile operation systems and mobile applications. The application layer provides users with an interface to operate their mobile devices. The operation system act as a platform to run mobile applications. Application-level issues usually take place in a multi-tenant environment or in a virtualized world[@hermann2014comparison]. There are six independent variables related to the application which might affect the perceived ES security:

@@

### Data Level Security Issue features
Since there is currently no appropriate regulation around data protection, data-level security is relying heavily on trust between the business and the provider. Data location and replication is one of the biggest concerns in the data level. A replica might be located in different countries where there is no clear legislation about data security and privacy, increasing the difficulty of managing the data [@kouatli2014comparative]. There are six independent variables related to the data access which might affect the perceived ES security:

@@

### Treatment effect result
Table \@ref(tab:model1) shows the treatment effect. In this model result, the intercept (5.377) represents the average effect for the reference group. There is only one reference group : **Treat: treat 0 (using Android devices)**The coefficient for **treatment effect** is -0.294, suggesting that the average perceived security from people who use iPhone is on average 0.294 unit lower than those who use Android, holding other variables constant. The p value is 0.0734, which indicates this is a significant result.

```{r model1,fig.cap = "regression model result",echo=FALSE, warning=FALSE,fig.width=5, fig.height=8}
## regression

propensity_score_regression1 <- lm(PSave~ treat,
                                  data = dta_m)
library(modelsummary)
ms<-
modelsummary(
propensity_score_regression1,
output = "default",
fmt = 3,
estimate = "estimate",
statistic = "std.error",
vcov = NULL,
conf_level = 0.95, #confidence level to use for confidence intervals
stars = TRUE,
align = NULL,
notes = NULL,
title = "Treatment effect")
ms%>%
  kableExtra::kable_styling(bootstrap_options = "basic",
                            latex_options = "HOLD_position",
                            table.envir = "table",
                            font_size =5
                       )

### regression model results

@@

@@

The coefficient for **weak_authentication** is -0.155, suggesting that one unit increase in weak_authentication score is associated with 0.155 unit decrease in the perceived ES security, holding other variables constant.The p value is 0.021122, which indicates this is a significant result.

```{r model,fig.cap = "regression model result",echo=FALSE, warning=FALSE,fig.width=5, fig.height=8}
## regression

propensity_score_regression <- lm(PSave~ Install_firewall+BYOD+ Ignore_warnning+Strong_pin+
                                    Store_passwords+update_OS+public_WiFi+unsecured_network+
                                    network_control+network_attack+encrypted_transimittion+unreliable_int+
                                    cloud_resource +cloud_compute+remote_datastore+Data_regulation+multiple_login+
                                    weak_authentication+unknown_app+  update_ES+ Auto_update+
                                    VPN + third_party_app+update+single_authenticate+audit_log+access_right+ change_data+ malicious_attack +Data_threats,
                                  data = dta_m)

propensity_score_regression1 <- lm(PSave~ treat,
                                  data = dta_m)

library(modelsummary)
ms<-
modelsummary(
propensity_score_regression,
output = "default",
fmt = 3,
estimate = "estimate",
statistic = "std.error",
vcov = NULL,
conf_level = 0.95, #confidence level to use for confidence intervals
stars = TRUE,
align = NULL,
notes = NULL,
title = "Regression results summary table")
ms%>%
  kableExtra::kable_styling(bootstrap_options = "basic",
                            latex_options = "HOLD_position",
                            table.envir = "table",
                            font_size =5
                       )

@@

Through the multiple linear regression, the treatment effect (treat1) is -0.294, which means using iPhone as device to operate enterprise system would be less secured than using Android. The p value is 0.07, which provide a strong evidence to support the regression result. Our guess that iPhone user would be more secured is rejected. In other word, using Android device would increase the perceived ES security. Android users have better awareness to defend different security issues.

@@

### Android user's average perceived ES security is higher!

From the result of the two sample T test, we are amazed to find the score for Android user's average perceived ES security is around 6%  higher than iPhone user's score. The sample distribution shows employees who have more than 3 years working experience more inclined to use Android phones. While for those employees with less than 1 year working experience, they are the majority iPhone users. Android users has better awareness towards the security issues might have the following reasons:  Apple think what is the best for you, and no matter what you need or not. So iPhone locks down the UI and system setting, which greatly limit the customization. In contrast, users can make their Android phone unique! With deep knowledge, users can make their Android phone more secured.

@@

* Do not use public Wi-Fi to operate any mobile Enterprise system (such as Wi-Fi in coffee shops, airport kiosks or other hotspots).
* Pay attention to wireless network security warnings that pop up on mobile devices
* Keep your web browser, wireless firewall, and anti-virus software up to date.

@@

@@

## Appendix A 
The data collection was done in China, so the language is Chinese. Here is the link: https://www.wjx.cn/jq/43537868.aspx

```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
library(here)
knitr::include_graphics(here::here("outputs/image/questionnaire1.png"))
```

## Appendix B 
The first 20 rows of raw data which will be used in regression is shown in the Table below. (Table \@ref(tab:rowdata))
#plot row data set in table
```{r rowdata, echo=FALSE}
  head(clean_data,20)%>%
  kableExtra::kbl(caption = "First 100 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
\newpage
